Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2019-01-21 AnalyticStructure_main.tex
update of supplementary and paper

\begin{figure}[ht]
\includegraphics[scale=0.6]{Fig4_CO_dos_rev1.eps}
\caption{(Color online) DOS of $CO$ excitation energies $\Omega_a$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations. The first IP threshold is depicted as the vertical dashed line.}
\label{CO_exc}
\end{figure}
\begin{figure}[ht]
\centering
\subfloat[Excitation landscape]
{\label{c6h6_excLand}
\includegraphics[scale=0.56]{Fig5a_C6H6_excLandscape.eps}} \\
\centering
\subfloat[DOS of Excitation energies]
{\label{C6H6_exc}
\includegraphics[scale=0.58]{Fig5b_C6H6_dos_rev1.eps}}
\caption{(Color online) Benzene molecule. (a): Excitation Landscape: the excitations have been separated in discrete and continuum sector following the criteria of Sec.~\ref{ExcitationLandscape}. (b): DOS of excitation energies $\Omega_a$. The first IP threshold is depicted as the vertical dashed line.}
\end{figure}

@@

We have analyzed the fulfillment of Eq.~\eqref{sminus2} for molecules of various
sizes and symmetries.
In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison for the $CO$ and $C_{60}$ molecules.
We notice that a considerable number of pseudo-continuum excitations is required
to find the correct result; the sector of the discrete excitations, even though
parametrized by localized, observable (in the sense of reproducible) excited states,
appears to be largely insufficient to express the reference fluctuation state. Its contribution is even negligible w.r.t.
the one coming from the continuum sector.

@@

This scenario can be also found for the other molecules presented in Table \ref{alphaTable};
varying the molecule size and symmetry does not modify the qualitative behavior of the excitation landscape. In addition the
localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$.
Such considerations are independent on the number of atoms of the molecule, as the range in $\omega$ needed to
achieve satisfactory agreement is largely above the last valence ionization threshold, which is
an intensive quantity.

>>>>

\begin{figure}[ht]
\includegraphics[scale=0.6]{Fig4_CO_dos_rev1.eps}
\caption{(Color online) DOS of $CO$ excitation energies $\Omega_a$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations. The first IP threshold is depicted as the vertical dashed line.}
\label{CO_exc}
\end{figure}
\begin{figure}[ht]
\centering
\subfloat[Excitation landscape]
{\label{c6h6_excLand}
\includegraphics[scale=0.56]{Fig5a_C6H6_excLandscape.eps}} \\
\centering
\subfloat[DOS of Excitation energies]
{\label{C6H6_exc}
\includegraphics[scale=0.58]{Fig5b_C6H6_dos_rev1.eps}}
\caption{(Color online) Benzene molecule. (a): Excitation Landscape: the excitations have been separated in discrete (black circle) and continuum (blue square) sectors following the criteria of Sec.~\ref{ExcitationLandscape}. (b): DOS of excitation energies $\Omega_a$. The first IP threshold is depicted as the vertical dashed line.}
\end{figure}

@@

We have analyzed the fulfillment of Eq.~\eqref{sminus2} for molecules of various
sizes and symmetries.
In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison for the $CO$ and $C_{60}$ molecules.
We notice that, in both the cases, a considerable number of pseudo-continuum excitations is required
to find the correct result; the sector of the discrete excitations
%, even though parametrized by localized, observable (in the sense of reproducible) excited states,
appears to be largely insufficient to express the reference fluctuation state. In particular, in the case of $CO$, the contribution of localized excitations is even negligible w.r.t. the one coming from the continuum sector.

@@

%This scenario can be also found for the other molecules presented in Table \ref{alphaTable};
This scenario is confirmed by the results for the other molecules presented in Table \ref{alphaTable};
varying the molecule size and symmetry does not modify the qualitative behavior of the excitation landscape (for further details
about the dependence of the excitation landscape on the size of the molecule see the supplementary material). In addition the
localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$.
Such considerations are independent on the number of atoms of the molecule, as the range in $\omega$ needed to
achieve satisfactory agreement is largely above the last valence ionization threshold, which is
an intensive quantity.

### 2019-01-21 Supplementary_material.tex
update of supplementary and paper

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\al}{\alpha}
\newcommand{\br}{\bar{\rho}}
\newcommand{\bg}{\bar{g}}
\newcommand{\bpi}{\bar{\pi}}

@@

\section*{Supplementary}

As stated in the main text we have investigated the effects of the size and dimension of a molecule in terms of the multi-threshold
structure of the excitation landscape. 
We may affirm that the number of localized excitations above the first ionization potential of the molecule typically grows with the
number of atoms of the molecule. This is simply due to the fact the bigger molecules behave as wider potential well and so the number of
(localized) empty KS states grows with the size....

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Aflatoxin_ExcitationLandscape.eps} 
        \caption{Aflatoxin} \label{fig:a}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{C60_ExcitationLandscape.eps} 
        \caption{$C_{60}$} \label{fig:b}
    \end{subfigure}

%     \vspace{1cm}
%     \begin{subfigure}[t]{\textwidth}
%     \centering
%         \includegraphics[width=\linewidth]{example-image-c.pdf} 
%         \caption{Price regulation} \label{fig:timing3}
%     \end{subfigure}
    \caption{Some general caption of all the figures....}
\end{figure}

>>>>

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

@@

\section*{Supplementary material}

We report the results of the excitation landscape for the $C_{60}$ and the Aflatoxin molecules. This analysis allows us to investigate the multi-threshold structure for systems with larger number of atoms and/or lower degrees of symmetry respect to the ones presented in the main text. The plots of Fig. \ref{exc-land} evidence that, in both the cases, the sector of localized excitations is very rich and extends well above the first ionization potential of the molecule. These results provide a further confirmation of the behavior already observed in the Table I.

The growth of the localized sector with the number of atoms of the molecule seems to be a general feature. It can simply explained by observing that bigger molecules behave as wider potential wells and possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range. In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq. (17) and the associated energy is parametrized as $\Omega_a=\epsilon_a-\epsilon_p$. In this case to the increase of the energy range spanned by the localized orbitals it directly corresponds a richer sector of localized excitations.
When $\op V'$ is switched on the excitation modes are expressed as a combination of KS orbitals but the presence of a high number of localized orbitals allows for a rich sector of localized excitations, as confirmed by the results of Fig. \ref{exc-land}.

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{C60_ExcitationLandscape.eps} 
        \caption{$C_{60}$} \label{fig:b}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Aflatoxin_ExcitationLandscape.eps} 
        \caption{Aflatoxin} \label{fig:a}
    \end{subfigure}
    \caption{Excitation landscape for the $C_{60}$ (panel a) and the Aflatoxin (panel b) molecules computed accordingly to the procedure described  in the appendix C. Black circles represent the localized sector and blue squares describe the pseudo-continuum one. }
\label{exc-land}
\end{figure}
